UKB Simulation Analyses

### 2023-12-05 ukb_sim.site_analyses.Rmd
cleaning up section headers

---
title: "proof-of-concept_mods"
output: html_document
date: '2023-10-06'
---

## QUESTIONS
- effect size for poly(age_days, 3) in gam/gamlss
- Fix age -> diff in male and female variance/intercept

@@

source("./R_scripts/gamlss_helper_funs.R")
# 
# # Enable this universe
# options(repos = c(
#   ggseg = 'https://ggseg.r-universe.dev',
#   CRAN = 'https://cloud.r-project.org'))
# 
# # Install some packages
# install.packages('ggsegExtra')
```

# Analysis Outline
## Load Data

@@

vol_list_global <- readRDS(file="R_scripts/vol_list_global.rds")
vol_list_regions <- readRDS(file="R_scripts/Vol_list_regions.rds")
sa_list <- readRDS(file="R_scripts/SA_list.rds")
ct_list <- readRDS(file="R_scripts/CT_list.rds")
pheno_list <- readRDS(file="R_scripts/pheno_list.rds")
```

## Basic Models
Designate *basic* model formula

```{r}
basic.m1 <- gamlss(formula = GMV ~ poly(age_days, 3) + sexMale,
                       sigma.formula = ~ poly(age_days, 3) + sexMale,
                       nu.formula = ~ 1,
                       family = BCCG, data=ukb_df_age.filt, trace = FALSE)
summary(basic.m1)
```

```{r}
#plot_singlestudy_centiles(basic.m1, "GMV", ukb_df_age.filt, "sexMale")
```

# Review Results

@@

### Raw Data Results

@@

### Combat Effects

#### Site Effects
Loading combatted data (scp'd from cubic: `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/data/ukb_to_model/*.csv' ./data/ukb_to_model`) to see how values change with different combat methods
```{r}
data.csvs <- list.files(path = "data/ukb_to_model", pattern = ".csv", full.names = TRUE)
combined_data <- data.frame()

@@

#### Centiles

@@

@@

#### Z-Score
calc how much z-scores change

>>>>

---
title: "UKB Simulation Analyses"
output: html_document
date: '2023-10-06'
---

@@

source("./cubic_scripts/R_scripts/gamlss_helper_funs.R")
# 
# # Enable this universe
# options(repos = c(
#   ggseg = 'https://ggseg.r-universe.dev',
#   CRAN = 'https://cloud.r-project.org'))
# 
# # Install some packages
# install.packages('ggsegExtra')
```

## Load

@@

vol_list_global <- readRDS(file="cubic_scripts/R_scripts/vol_list_global.rds")
vol_list_regions <- readRDS(file="cubic_scripts/R_scripts/Vol_list_regions.rds")
sa_list <- readRDS(file="cubic_scripts/R_scripts/SA_list.rds")
ct_list <- readRDS(file="cubic_scripts/R_scripts/CT_list.rds")
pheno_list <- readRDS(file="cubic_scripts/R_scripts/pheno_list.rds")

aseg_cerebrum <- readRDS(file="/Users/megardn/Desktop/BGD_Repos/ggseg_atlas/aseg_cerebrum_atlas.RDS")
```

@@

## Raw Data Results
Review outcomes from raw (non-ComBat-ed) data

@@

## ComBat Effects by Moment

Loading combatted data (scp'd from cubic: `scp -r 'gardnerm@cubic-login.uphs.upenn.edu:/cbica/home/gardnerm/combat-biovar/data/ukb_to_model/*.csv' ./data/ukb_to_model`) to see how values change with different combat methods

```{r}
data.csvs <- list.files(path = "data/ukb_to_model", pattern = ".csv", full.names = TRUE)
combined_data <- data.frame()

@@

## ComBat Effects on Centiles

@@

#### Sex-Biases

@@

## ComBat Effects on Z-Score
calc how much z-scores change
